A systematic search for transiting planets in the \KT\ data

### 2015-02-13 ms.tex
words about completeness

\newcommand{\period}{{\ensuremath{P}}}
\newcommand{\phase}{{\ensuremath{T^0}}}
\newcommand{\duration}{{\ensuremath{D}}}
\newcommand{\depth}{{\ensuremath{Z}}}
\newcommand{\transittime}{{\ensuremath{T}}}
\newcommand{\impact}{{\ensuremath{b}}}
\newcommand{\ecc}{{\ensuremath{e}}}
\newcommand{\pomega}{{\ensuremath{\varpi}}}

@@

\title{%
    A systematic search for transiting planets in the \KT\ data % hogg changed title!
}

@@

The noise floor for \kepler\ data is often quoted as 15 parts per million (ppm) per
six hours of observations \citep{Gilliland:2011}.
Although they generally do not interfere with searches for transiting
planets, larger systematic effects exist on different timescales.
One of the most serious of these is spacecraft pointing: If the detector
flat-field is not known with very high accuracy, then tiny changes to the relative
illumination of pixels caused by a star's motion in the focal plane will lead
to changes in the measured or inferred brightness of the star.

The great stability of the original \kepler\ Mission
came to an end with the failure of a critical reaction wheel.
The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary Mission,
observing about a dozen fields near the ecliptic plane, each for
$\sim 75$ days at a time.
Because of the degraded spacecraft orientation systems, the new \KT\ data
exhibit far greater pointing variations---and substantially more
pointing-induced variations in photometry---than the original \kepler\ Mission data.
This makes good data-analysis techniques even more valuable.

Good photometry relies on either a near-perfect flat-field
and pointing model or else data-analysis techniques that are
insensitive to these instrument properties.
The flat-field for \kepler\ was measured on the ground before the launch of
the spacecraft, but is not nearly as accurate as required to make
pointing-insensitive photometric measurements at the relevant level of precision.
In principle direct inference of the flat-field might be possible;
however, because point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth, there isn't enough information in the data to derive or
infer a complete or accurate flat-field map.
Therefore, work on \KT\ is sensibly focused on building data-analysis
techniques that are pointing-insensitive.

@@

The alternative to this approach is to \emph{simultaneously fit} both the systematics
and the transit signals.
Simultaneous fitting can push the detection limits to lower signal-to-noise while
robustly accounting for uncertainties about the systematic trends.
In particular, it permits us to \emph{marginalize} over choices in the noise
model and propagate any uncertainties about the systematic effects
to our confidence in the detection.
\dfmtodo{Do we need more about marginalization here?}

@@

To generate the synthetic signals, we follow the following procedure:
\begin{enumerate}

{\item draw the number of transiting planets based on the observed
multiplicity distribution of KOIs (CITE),}

{\item for each planet, choose limb darkening parameters, orbital periods,
phases, radius ratios, impact parameters, eccentricity, and argument of
periapsis, from the distributions listed in \tab{dist}}

\end{enumerate}

These synthetic systems have periods and radius ratios drawn uniformly in
\dfmtodo{some range} and uniformly distributed impact parameters and phases.
The eccentricities are drawn from a beta distribution with \dfmtodo{some
parameters; cite Kipping} and the multiplicity is set to match the observed
multiplicity distribution in the KOI catalog \dfmtodo{cite}.
MA limb darkening, exposure time integration, etc.

After running these light curves with injections through the full pipeline, if
the resulting period and phase of the recovered signal were within YYYY of the
true injected values, we deemed the injection a success.
\Fig{completeness} shows the fraction of recovered signals as a function of the
physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.

>>>>

\newcommand{\period}{{\ensuremath{P}}}
\newcommand{\phase}{{\ensuremath{T^0}}}
\newcommand{\duration}{{\ensuremath{D}}}
\newcommand{\depth}{{\ensuremath{Z}}}
\newcommand{\transittime}{{\ensuremath{T}}}
\newcommand{\impact}{{\ensuremath{b}}}
\newcommand{\ecc}{{\ensuremath{e}}}
\newcommand{\pomega}{{\ensuremath{\omega}}}

@@

\title{%
    A systematic search for transiting planets in the \KT\ data
}

@@

The noise floor for \kepler\ data is often quoted as 15 parts per million per
six hours of observations \citep{Gilliland:2011}.
Although they generally do not influence the ability to search for transiting
planets, larger systematic effects exist on different timescales.
One of the most serious of these is spacecraft pointing: If the detector
flat-field is not known \emph{exquisitely}, then tiny changes to the relative
illumination of pixels caused by a star's motion in the focal plane will lead
to changes in the measured or inferred brightness of the star.

The pointing of \kepler\ was stable at the (LEVEL) level (citation) throughout
the primary mission.
This stability came to an end with the failure of a critical reaction wheel.
The \KT\ Mission \citep{Howell:2014} is a follow-on to the primary \kepler\
Mission, observing about a dozen fields near the ecliptic plane, each for
$\sim 75$ days at a time.
Because of the degraded spacecraft orientation systems, the new \KT\ data
exhibit far greater pointing variations---and substantially more
pointing-induced variations in photometry---than the original \kepler\ data.
This makes good data-analysis techniques even more valuable.

Good photometry relies on either a near-perfect flat-field
and pointing model or else data-analysis techniques that are
insensitive to such variations.
The flat-field for \kepler\ was measured on the ground before the launch of
the spacecraft, but is not nearly as accurate as required to make
pointing-insensitive photometric measurements at the relevant level of precision.
In principle direct inference of the flat-field might be possible;
however, because point sources are observed with relatively limited
spacecraft motion, and only a few percent of the data are actually stored and
downloaded to Earth, there isn't enough information in the data to derive or
infer a highly accurate flat-field map.
Therefore, work on \KT\ is sensibly focused on building data-analysis
techniques that are pointing-insensitive.

@@

The alternative to this approach is to simultaneously fit both the systematics
and the transit signals.
This method can push the detection limits to lower signal-to-noise while
robustly accounting for uncertainties about the systematic trends.
In particular, this allows us to \emph{marginalize} over choices in the noise
model and propagate any uncertainties to our confidence in the detection.
\dfmtodo{Do we need more about marginalization here?}

@@

To generate the synthetic signals, we use the following procedure:
\begin{enumerate}

{\item Draw the number of transiting planets based on the observed
multiplicity distribution of KOIs (CITE).}

{\item Sample---from the distributions listed in
\tab{dist}---limb darkening parameters and, for each planet, an orbital
period, phase, radius ratio, impact parameter, eccentricity, and argument of
periapsis.}

{\item Based on the chosen physical parameters, simulate the light curve,
taking limb darkening and integration time into account \citep{ma,
kipping-int}, and multiply it into the raw aperture photometry.}

\end{enumerate}
We then process these light curves using exactly the pipeline that we use for
the light curves without injections.
Finally, we test for recovery after applying the cuts in signal-to-noise and
period.
We should, of course, also process the results of the injection tests by hand
to ensure that our measurements of detection efficiency aren't biased by this
step but, since we chose to limit our sample to very high signal-to-noise
candidates, it seems unlikely that our hand vetting removed any true transit
signals.
Any estimates of the false alarm rate will, however, be affected by this
negligence but we leave a treatment of this for future discussion.

\Fig{completeness} shows the fraction of recovered signals as a function of
the physical parameters of the injection and the magnitude of the star.
As expected, the shallower transits at longer periods are recovered less
robustly.
